---
title: "Penguins ANOVA"
author: "Robert Saldivar"
date: "November 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read-in penguins.csv data

```{r, include = FALSE}

library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

Our question:

Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gengtoo, and Adelie)?

2. Do some exploring 

New functions: with + table for easy counting over multiple factors

Update species name using case_when

```{r}
counts <- with(penguins, table(species, sex))

penguins2 <- penguins %>%
  mutate(common_name = 
           case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
           )) %>%
  select(-species) %>%
  filter(sex=="FEMALE")
```

-Exploratory graphys
-Summary statistics
-Levene's tests for equal variances
-one-way ANOVA
-post-hoc testing

```{r}
hist <- ggplot(penguins2, aes(x= flipper_length)) +
  geom_histogram(aes(fill = common_name)) +
  facet_wrap(~ common_name)

hist

qq <- ggplot(penguins2, aes(sample = flipper_length)) +
  geom_qq() +
  facet_wrap(~common_name)

qq

# Levene's test for equal variance (> 2 group... if y9ou have two groups, use the F-test for equal variances)

# We'll use the funtionT leveneTest from the 'car' package

#H0: Variances are equal
#HA: Variances are unequal

penguin_levene <- leveneTest(flipper_length ~ common_name, data = penguins2)
penguin_levene

# We retain the null hypothesis of equal variances(p = 0.06)

variances <- penguins2 %>%
  group_by(common_name) %>%
  summarise(
    variances = var(flipper_length)
  )

variances

```

